Prehensile Manipulation Planning: Modelling, Algorithms and Implementation

### 2020-10-09 hpp.tex
Update hpp.tex.

Some systems are subject to non-linear constraints. These non-linear
constraints define a sub-manifold of the configuration space the robot must
stay on. For instance, legged robots that must keep contact with the
ground and enforce quasi-static equilibrium, or multi-arm systems
grasping a same object are subject to this type of constraints. As the
volume of the constrained manifold is usually equal to zero, sampling
random configurations satisfying the constraints is an event of zero
probability. To sample configurations on the constrained manifold,
\cite{DalNakLamLau2009} and \cite{berenson2011} project random
configurations using a generalization of Newton-Raphson
algorithm. Another way to sample configurations on a constrained
manifold consists in expressing some configuration variables with
respect to others~\cite{Cortes2002}, \cite{MirLam2018} when this is
possible. \cite{atlasRRT} propose another method based on non-linear
projection. They cover the constrained manifold by growing an atlas
composed of local charts. This approximation provides a probability
distribution that is closer to the uniform distribution over the
manifold than the projection of a uniform distribution over the
configuration space. \cite{tb-rrt2016} propose a variation of the latter paper.
The main difference resides in the fact that the nodes
built on the tangent space are not immediately projected on the manifold.
\cite{KinMolKav2019} provide a rich overview
of the various approaches to motion planning with non-linear
constraints.

@@

Rearrangement planning \cite{ota2004rearrangement}, \cite{LIS210},
\cite{KroBek2015}, \cite{LerPha2015} consists in finding a sequence of
manipulation paths that move some objects from an initial pose to a
final pose. The final configuration of the robot is not specified. A
simplifying asumption is the existence of a monotone solution, that is
a solution where each object is grasped once only and is moved from
its initial pose to its final pose \cite{stilman2008planning},
\cite{stilman2007manipulation}, \cite{srivastavaetal2014icra}, \cite{nieuwenhuisen2008effective},
\cite{ota2004rearrangement}. They mostly use two-level methods
composed of a symbolic or task planner and of a motion
planner~\cite{cambon:hal-01976081}.

@@

@@

\subsection{Waypoint transitions}

@@

>>>>

Some systems are subject to non-linear constraints. These non-linear
constraints define a sub-manifold of the configuration space the robot must
stay on. For instance, legged robots that must keep contact with the
ground and enforce quasi-static equilibrium, or multi-arm systems
grasping a same object are subject to this type of constraints. As the
volume of the constrained manifold is usually equal to zero, sampling
random configurations satisfying the constraints is an event of zero
probability. To sample configurations on the constrained manifold,
\cite{DalNakLamLau2009} and \cite{berenson2011} project random
configurations using a generalization of Newton-Raphson
algorithm. Another way to sample configurations on a constrained
manifold consists in expressing some configuration variables with
respect to others~\cite{Cortes2002}, \cite{MirLam2018} when this is
possible. \cite{atlasRRT} propose another method based on non-linear
projection. They cover the constrained manifold by growing an atlas
composed of local charts. This approximation provides a probability
distribution that is closer to the uniform distribution over the
manifold than the projection of a uniform distribution over the
configuration space. \cite{tb-rrt2016} propose a variation of the latter paper.
The main difference resides in the fact that the nodes
built on the tangent space are not immediately projected on the manifold.
\cite{CefOri2019} propose a general framework to plan task constrained motions
in the presence of moving obstacle.
\cite{KinMolKav2019} provide an in-depth review of the various approaches to
motion planning with non-linear constraints.

@@

Rearrangement planning \cite{ota2004rearrangement}, \cite{LIS210},
\cite{KroBek2015}, \cite{LerPha2015} consists in finding a sequence of
manipulation paths that move some objects from an initial pose to a
final pose. The final configuration of the robot is not specified. A
simplifying asumption is the existence of a monotone solution, that is
a solution where each object is grasped once only and is moved from
its initial pose to its final pose \cite{stilman2008planning},
\cite{stilman2007manipulation}, \cite{srivastavaetal2014icra}, \cite{nieuwenhuisen2008effective},
\cite{ota2004rearrangement}. They mostly use two-level methods
composed of a symbolic or task planner and of a motion
planner~\cite{cambon:hal-01976081}, \cite{KaeLoz2013}, \cite{18-toussaint-RSS}.

@@

Our work shares many ideas with \cite{HauNgt2011} where the notion of constraint
graph is present, although not as clearly expressed as in this paper. The main
contribution of our work with respect to this latter paper is that the
constraint graph is built automatically at the cost of a more restricted range
of applications. We address indeed only prehensile manipulation.

@@

\subsection{Waypoint transitions}\label{subsec:waypoint}

@@

\subsubsection{Influence of waypoint transitions}

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{figures/ur5-grasps-pokeball.png}
  \end{center}
  \caption{UR-5 robot manipulating a ball lying on a plane. The robot is requested to pick the ball and place it a few centimeters aside.}
  \label{fig:ur5-pokeball}
\end{figure}

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|l|l|l|}
    \hline
    & min & max & mean & std dev \\
    \hline
    with waypoints&&&&\\
    time (s) & 0.01 & 0.49 & 0.12 & 0.14 \\
    nodes & 4 &  30 & 9.75 & 7.26\\
    \hline
    without waypoints&&&&\\
    time (s) & 4.15 & 73.53 & 26.24 & 17.07 \\
    nodes & 97 &  1609 & 711.55 & 407.98\\
    \hline
  \end{tabular}
  \end{center}
  \caption{UR-5 manipulating a box with and without waypoint transitions}
  \label{tab:waypoint}
\end{table}

All the previous experimental results have been obtained using
waypoint transitions as described in Section~\ref{subsec:waypoint}. We
now empirically show the positive effect of waypoints on the the
efficiency of manipulation planning. For that, we run 20 times
Algorithm M-RRT on the same problem with and without waypoint
transitions.  The problem is defined by a UR-5 robot manipulating a
ball as shown in Figure~\ref{fig:ur5-pokeball}. The results are
reported in Table~\ref{tab:waypoint}. We can notice that for this
example, the waypoint transitions make the time of computation and the
number of nodes decrease by 2 orders of magnitude. This can be
explained by the fact that in grasp configurations, the gripper is
very close to the object and only a small part of the approaching
directions of the gripper toward the object leads to collision-free
paths. Waypoint states on the contrary are away from obstacles and
easier to reach. The transition between the pregrasp waypoint and the
grasp $\cap$ placement waypoint is always collision-free.
